Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-11-17 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
10k FE experiment

We found that the JavaScript ecosystem is mature enough for developing non-trivial 
code, but developers have to consider the differences betwwen VMs implementations
and also use certain libraries in order to increase the precision and repeatability of
algorithms. As for the performance of the JavaScript implementaion against Java and Matlab
we conducted first the basic test described earlier in a 3.7 GHz Quad-Core Intel Xeon E5 processor running OS X 10.10.5, 
using Java(TM) SE Runtime Environment (build 1.8.0\_25-b17), 
MatLab version R2015a for Mac OSX, Node FrameWork version 0.12.2, Google Chrome Version 46.0.2490.86 (64-bit) 
and Firefox version 41.0.2. The performance of the time required for 10,000 FEs is presented in Figure \ref{fig:f15_times}.
In our test the Matlab implementation had the best performance with an average of 935ms, followed by Java with
991ms, JavaScipt took 35\% more time than Java with 1,270ms using Node.js and 1279ms in Chrome. 
The results also show that there is not much difference between the Node.Js implemenation an that of a
browser. There is also not much difference between running the code in the main thread or as workers, but
when running the experiment in Firefox a dialog alerted of the script taking to long, showing that this
kind of processing is not intended for the main thread.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\linewidth]{f15_times.png}
\caption{ Runtime of 10,000 function evaluations (FEs) for $F_{15}$} 
\label{fig:f15_times}
\end{figure}

>>>>

We found that the JavaScript ecosystem is mature enough for developing non-trivial 
code, but developers have to consider the differences betwwen VMs implementations
and also use certain libraries in order to increase the precision and repeatability of
algorithms. As for the performance of the JavaScript implementaion against Java and Matlab
we conducted first the basic test described earlier in a 3.7 GHz Quad-Core Intel Xeon E5 processor running OS X 10.10.5, 
using Java(TM) SE Runtime Environment (build 1.8.0\_25-b17), 
MatLab version R2015a for Mac OSX, Node FrameWork version 0.12.2, Google Chrome Version 46.0.2490.86 (64-bit) 
and Firefox version 41.0.2. The performance of the time required for 10,000 FEs is presented in Figure \ref{fig:f15_times}.
In our test the Matlab implementation had the best performance with an average of 935ms, followed by Java with
991ms, JavaScipt took 32\% more time than Java with 1240ms in Chrome using a Web Worker and 1,270ms using Node.js. 
The results also show that there is not much difference between the Node.Js implemenation an that of a
browser. There is also not much difference between running the code in the main thread or as workers, but
when running the experiment in Firefox a dialog alerted of the script taking to long, showing that this
kind of processing is not intended for the main thread. Also there is not much diference when running two
Web Workers in parallel taking 1279ms each. This experiment shows that JavaScript is viable 
language for developing complex mathematical functions for running in the browser. 
\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\linewidth]{f15_times.png}
\caption{ Runtime of 10,000 function evaluations (FEs) for $F_{15}$} 
\label{fig:f15_times}
\end{figure}
